# Study on Android Games

## Introduction

### Where and how the dataset is gathered?

This dataset, *Top Games on Google is  through [Kaggle](https://www.kaggle.com/datasets) by searching the keyword *videogames*.
Dataset Top Games on Google Play Store was collected by **Dhruvil Dave** through **Google Play Store** directly. He gathered these information by collecting the information shown in the game details page.This dataset was gathered around *Jun 2021*,containing 100 games and 17 game-types categories available in in android Google Play.

### What is this study about

In this study, we focus on the correlation relationship among the category, the rating of each android games, and the installment of each android games. To focus on the 
which category is most popular, if its popularity is relevant with its rating (5stars rate), and if the growth of installment is relevant with the rating.
Three charts, ,are included in order to answer these questions. The first chart focuses on . The second chart focus on . The third charts is focus on .


### Summary information

The variables we choose is category and rating.
```{r include = FALSE}
library(knitr)
library(dplyr)
library(kableExtra)
library(knitr)
android_games <- read.csv(file = "https://raw.githubusercontent.com/ShuhanChenrock/Info201_Final_Project/main/android-games.csv")

```

```{r}
mean_total_ratings <- android_games %>% group_by(category)%>% summarise (mean_num = mean(total.ratings)) %>% arrange(mean_num)

mean_total_ratings %>% kable() %>% kable_styling(latex_options = "striped")

```


```{r}

```
